Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-09-25 Latex/journal_v1/V6/pr.tex
add paper last version

In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and uRLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and uRLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. {\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the MAC/RLC functions in the O-DU logical node, the PDCP/SDAP functions in the O-CU-UP, and the UPF nodes. 
 There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of 
%pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs),
 $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.

@@

Assume the mean arrival data rate of the UPF layer for the slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,

@@

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

In sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 

@@

In this section, firstly we describe the initial points and the comparison algorithms.
Then we talk about the feasible region in our system. 
Afterward, we illustrated the numerical results.
\subsection{The initial Points and The Comparison Algorithms}
In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, uRLLC, and mMTC services.
Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{cell.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{O-RU placement in a cell}
  \label{fig:cell}
\end{figure}
Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.  Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution
and it is the Rayleigh fading channel between the UE and O-RU.
We consider 25 PRBs are used in the network and the
packet size is equal to 20 bytes.
The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the uRLLC  service is $\lambda  = 0.2Mbps$. 
Also the quantization noise is assumed to be $10^{-13}$.
Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.

The other parameters of these simulations are depicted in Table \ref{table:1a}.
\begin{table}
 \caption {Simulation Parameter} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Parameter & Value \\ [0.5ex]
  \hline\hline
  Noise power & -174dBm\\
  \hline
  Bandwidth & 180 KHz \\
  \hline
 Maximum transmit Power of each O-RU & 40dBm \\
  \hline
  Maximum delay for eMBB &  4msec \\
  \hline
    Maximum delay for uRLLC &  1msec \\
  \hline
  Maximum delay for mMTC &  5msec \\
  \hline
  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
   \hline
  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 
  \hline
   Minimum data rate for uRLLC and mMTC &  2 bits/sec/Hz \\ 
  \hline
   Maximum received power for mMTC &  20 dBm \\ [.5ex]   
  \hline
    Maximum received power for eMBB and uRLLC &  33 dBm \\ [.5ex]   
  \hline
 \end{tabular}
 \end{center}
 \end{table}

Finding a feasible initial value is almost tricky. To overcome this challenge, we use a fast method that we talk about it in the \ref{fr}. If the fast method converged and has a feasible solution, so our algorithm (IABV) can be converged too.

Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
 The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on distance. Also, the number of activated VNF for each slice is fixed. The optimal power
 is obtained using the CVX of Matlab, which used the successive convex approximation (SCA) method.

The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}. In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
\subsection{Feasible Region}\label{fr}
Applying the correct initial point to make the system feasible is a significant step in our work.
During the simulation, it can be noted that sometimes the algorithm does not converge for some of the iterations with fixed initial values.
To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters (such as number of UEs, the threshold of power and rate,... ) and random channel gains of UEs.
By comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain. One solution is to eliminate UEs who undermine system convergence.
For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interferences.
Another solution is to remove the simulations in the mont-Carlo that do not converge.
In the simulation part, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
the proposed algorithm (IABV). 
If the conditions \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
The FA algorithm is depicted as algorithm \ref{alg3}.
 \begin{algorithm}
\caption{Fast Algorithm to Check the Convergence (FA)}\label{alg3}
\begin{algorithmic}[1]
\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
\State Assume the number of PRBs is $K$
\State Assume $d_{r,u(s,i)}$ is the distance from the $r^{th}$ O-RU to the UE i in slice s
\State Set count = 0 
\State Set $p_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $e_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $g_{u(s,i)}^{r} = 0 \quad \forall r,s,i$
\For{$s \gets 1$ to $S$} 
\For{$i \gets 1$ to $U_s$}
\State count = count +1  
\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
\State $g_{u(s,i)} ^{r^*}=1$
\State temp =mod(count, K)            
\If {temp=0 }
\State $e_{r^*,u(s,i)}^{K} = 1 $
\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
\Else 
\State $e_{r^*,u(s,i)}^{temp} = 1 \quad \forall r$ 
\State Set $p_{r^*,u(s,i)}^{temp} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
\EndIf

>>>>

In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and uRLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and uRLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. {\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.

@@

Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,

@@

Assume UE $i$ in slice $s$, associated with O-RU $r$, is allocated to PRB $k$  (i.e., $e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,\\
\end{split}
\end{equation}
where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows:
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S, \\
      0 & \text{otherwise,}
    \end{cases}
\end{equation}
where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless of the services), that is associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 

@@

In this section, firstly, we describe the initial points and the comparison algorithms.
Then, we talk about the feasible region of our system model. Afterward, we illustrate the numerical results.

\subsection{The initial Points and The Comparison Algorithms}
In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, uRLLC, and mMTC services.
Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{cell.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{O-RU placement in a cell}
  \label{fig:cell}
\end{figure}
Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $, where $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution and it is the Rayleigh fading channel between the UE and O-RU.
We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.
The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the uRLLC  service is $\lambda  = 0.2Mbps$. 
Also, the quantization noise is assumed to be $10^{-13}$.
Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.
\begin{table}
 \caption {Simulation Parameters} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c | c ||}
  \hline
Parameter & Value \\ [0.5ex]
  \hline\hline
  Noise power & -174dBm\\
  \hline
  Bandwidth & 180 KHz \\
  \hline
 Maximum transmit Power of each O-RU & 40dBm \\
  \hline
  Maximum delay for eMBB &  4msec \\
  \hline
    Maximum delay for uRLLC &  1msec \\
  \hline
  Maximum delay for mMTC &  5msec \\
  \hline
  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
   \hline
  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 
  \hline
   Minimum data rate for uRLLC and mMTC &  2 bits/sec/Hz \\ 
  \hline
   Maximum received power for mMTC &  20 dBm \\ [.5ex]   
  \hline
    Maximum received power for eMBB and uRLLC &  33 dBm \\ [.5ex]   
  \hline
 \end{tabular}
 \end{center}
 \end{table}

Finding a feasible initial value is almost tricky. To overcome this challenge, we use a fast method that is discussed in \ref{fr}. If the fast method converges and has a feasible solution, so our algorithm (IABV) can be converged too.

Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
 The first one is a baseline scheme, which uses random PRB allocation. The association of O-RU is carried out based on distance. Also, the number of activated VNFs for each slice is fixed. The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method. The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}. In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
\subsection{Feasible Region}\label{fr}
Applying the correct initial point to make the system feasible is a significant step in our work.
During the simulations, it can be noted that sometimes the algorithm does not converge for some of the iterations with fixed initial values.
To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters (such as number of UEs, the threshold of power and rate,... ) and random channel gains of UEs.
By comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain. One solution is to eliminate UEs who undermine system convergence.
For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interference.
Another solution is to remove the simulations in the mont-Carlo that do not converge.
In the simulation part, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
the proposed algorithm (IABV). 
If the conditions in \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
The FA algorithm is represented in Algorithm \ref{alg3}.

 \begin{algorithm}
\caption{Fast Algorithm (FA) to Check the Convergence}\label{alg3}
\begin{algorithmic}[1]
\State The number of UEs: $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
\State The number of PRBs: $K$
\State the distance from the $r^{th}$ O-RU to the UE i in slice $s$: $d_{r,u(s,i)}$ 
\State Set count = 0 
\State Set $p_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $e_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $g_{u(s,i)}^{r} = 0 \quad \forall r,s,i$
\For{$s \gets 1$ to $S$} 
\For{$i \gets 1$ to $U_s$}
\State count = count +1  
\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
\State $g_{u(s,i)} ^{r^*}=1$
\State temp =mod(count, K)            
\If {temp=0 }
\State $e_{r^*,u(s,i)}^{K} = 1 $
\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
\Else 
\State $e_{r^*,u(s,i)}^{\text{temp}} = 1 \quad \forall r$ 
\State Set $p_{r^*,u(s,i)}^{\text{temp}} = \min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\} $
\EndIf

\State \textbf{end if}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}

The complexity order of this algorithm is $O(R\times \mathfrak{N})$ which is remarkably lower than the complexity order of the IABV method.
In the FA algorithm, the O-RU association is based on the distance of the UE to the O-RU. 
Each UE is associated with the nearest O-RU. Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{\max}, P_r^{\max}/\mathfrak{N}\}$).
Moreover, the allocation of PRBs to UEs is based on dividing the number of UEs by the total number of PRBs.
If the number of UEs is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
\subsection{Numerical Results}
In Fig. \ref{fig:1}, the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods. Suppose we have one service instance for each type of service, so we have three various services in this figure. Also, we have between 6 to 48 UEs in the system.
Here, we did not consider the priority. The figure presented that the proposed method, IABV, is $18.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increases. Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{Arate_ue1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate throughput vs. number of UEs for each service in the presence of three services}
  \label{fig:1}
\end{figure}
%Assume we have two type of services (uRLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services uRLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
%The figure \ref{fig:2}, presented that by increasing the priority factor for uRLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput for mMTC and uRLLC vs. Priority of uRLLC }
%  \label{fig:2}
%\end{figure}
%In figure \ref{fig:3}, the total sum rate of uRLLC and mMTC is shown vs. priority of uRLLC. It is shown that the proposed method is much better than the baseline scheme. 
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{sumRatePri.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput of all services vs. Priority of uRLLC}
%  \label{fig:3}
%\end{figure}

Figure \ref{fig:4} depicts the number of activated VNFs for five different mean service times of one uRLLC service vs. the mean arrival time for 12 UEs. This figure presents that as the mean arrival rate increases, the number of activated VNF increases. Moreover, the number of activated VNFs decreases when the mean service rate increases.
